%======================================================================
\section{Conclusion}
\label{sec:conclusion}
%======================================================================

We presented the first large-scale empirical study of security vulnerabilities in LLM-generated smart contracts. Our analysis of 1,800 contracts across six state-of-the-art LLMs---GPT-4o, Claude 3.5 Sonnet, Gemini 2.5 Flash-Lite, DeepSeek Coder V2, Qwen 2.5 Coder 32B, and CodeLlama-34B---reveals that 72.7\% of compilable contracts contain at least one vulnerability, with 28.5\% containing high-severity flaws that could lead to direct financial loss. Significant variation exists across models, with compilation rates ranging from 90.0\% (GPT-4o) to 34.7\% (CodeLlama) and the largest pairwise effect size between Claude and CodeLlama (Cliff's $\delta = 0.63$).

Our most striking finding is the adversarial null result: adversarial prompts do not increase vulnerability rates compared to standard prompts. In fact, standard prompts produce significantly more vulnerabilities (mean 5.02 vs.\ 3.39, $p < 0.001$), because adversarial prompts tend to produce smaller, simpler contracts. This implies that vulnerabilities are \emph{intrinsic} to LLM code generation---arising from patterns in training data rather than from prompt manipulation---and cannot be mitigated through prompt engineering alone. We also identified three LLM-specific vulnerability patterns---phantom guards, inherited vulnerabilities, and context window degradation---suggesting the need for LLM-aware security tooling.

These findings have immediate practical implications: developers must not deploy LLM-generated smart contracts without rigorous multi-tool security auditing, LLM providers should prioritize security-aware code generation for high-stakes domains, and the security community should develop detection capabilities targeting LLM-specific vulnerability patterns.

We release our full dataset, analysis pipeline, and vulnerability taxonomy to support reproducibility and future research. Future work includes extending the study to additional LLMs and newer model versions, smart contract languages (Rust/Solana, Move/Aptos), runtime analysis through fuzzing, multi-turn interactive generation sessions, comparison with human-written baselines, and the development of LLM-aware security tools that can detect the novel vulnerability patterns we have identified.
